---
title: |
    | STAT 408: Midterm Exam
    | Name:
output: pdf_document 
---

```{r setup, include=FALSE}
library(knitr)
library(tibble)
library(dplyr)
knitr::opts_chunk$set(eval = FALSE)
```

There are a total of 8 question. You only need to answer 7 of them. Put an __X__ through the question you don't want graded. If you answer all of the questions, Q8 will not be graded.

### Code interpretation
For questions 1 - 3 use the following data frame (called `snow`) and interpret the code. For full credit (and partial credit), write what the code will return along with justification for your answer.

```{r, eval = T, echo = F}
snow <- tibble(ski_hill = c('Big Sky','Jackson Hole','Taos','Bridger Bowl','Loveland', "Vail", "Park City"),
               pass = c('Ikon','Ikon','Ikon','Powder Alliance','Powder Alliance', "Epic","Epic"),
       acres = c(5800, 2500,1294, 2000, 1800, 5317,7300),
       vertical = c(4336, 4139,3281, 2600, 2210,3450,3226 ))
snow %>% arrange(pass) %>% kable()
```

## 1. (4 points)

```{r}
library(tidyverse)
snow %>% group_by(pass) %>% summarize(min_size = min(acres)) %>% arrange(min_size)
```

\vfill

## 2. (4 points)
```{r}
for (i in 1:5){
  print(snow$ski_hill[i])
    if (snow$pass[i] == 'Ikon'){
      print("is on the Ikon pass")
    } else {
      print("is not on the Ikon pass")
    }
}
```

\vfill

\newpage

## 3. (4 points)
```{r}
snow %>% ggplot(aes(y = vertical, x = acres, shape = pass)) +
  geom_point() + ggtitle('Vertical vs. Skiable Acres')
```

\vfill
\vfill
\vfill
\vfill
## 4. (4 points)
```{r}
ifelse(snow[,3] > 5000 | snow[,4] > 4000, 
       "The mountain is big or steep",
       "The mountain is not big or steep")
```

\vfill
\vfill
\newpage
For questions 5 and 6 use the `snow` data frame and the `ticket_price` data frame (below).
```{r, eval = T, echo = F}
ticket_price <- tibble(ski_hill = c('Big Sky','Bridger Bowl','Discovery'),
               pass_cost = c('1,699', '900', '525'))
ticket_price %>% kable()
```

## 5. (4 points)
```{r}
snow %>% inner_join(ticket_price, by = "ski_hill")
```
\vfill

## 6. (4 points)

```{r}
library(stringr)
ticket_price %>% mutate(cost = str_replace(pass_cost, ',', ''))
```
\vfill


\newpage

## 7. (4 points)
Describe at least two principles of good data visualization and include a sketch to demonstrate - you will not be graded on your artistic ability, but keep it neat.

\vfill

## 8. (4 points)
Finish the function. Either code or prose is acceptable.
```{r}
flip_coin <- function(num_flips){
  # Function to simulate flipping a fair coin
  # ARGS: num_flips - number of times to flip coin
  # RETURNS: vector of coin flips containing "H" or "T"
  
  
  
  
  
  
  
  
  
  
}
```




